%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Alexander Miranda}
\address{7721 16th Avenue NE\linebreak Seattle WA 98115}
\contacts{(407) 462-9753 \linebreak alexandermichaelmiranda@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer}{GenWest Systems Inc.}{2014 - Present}
			Front-end Engineer Principal for GNOME/ADIOS			
			\begin{itemize}
				\item 
				\item Implemented iChat integration with OS X Spotlight Search by creating tool which extracts metadata from saved chat transcripts and provides metadata to a system-wide search database.
				\item Redesigned chat file format and implemented backwards compatibility for search.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Teaching Assistant}{Code Fellows}{March 2014}	
			\begin{itemize}
				\item Assisted students learning web development with an emphasis in javaScript.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Philadelphi}{University of Pennsylvania}{Fall 2000 -- May 2005}
			\begin{itemize}
				\item M.S.E. in Computer and Information Science, May 2005. GPA: 3.6
				\item B.S.E. in Computer Science Engineering with Minor in Mathematics, May 2005.  In-major GPA: 3.4.
				\item Graduate Coursework: Software Foundations; Computer Architecture; Algorithms; Artificial Intelligence; Comparison of Learning Algorithms; Computational Theory.
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Engineering Entrepreneurship; Calculus III.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Multi-User Drawing Tool} (2004). Electronic classroom where multiple users can view and simultaneously draw on a “chalkboard” with each person’s edits synchronized.  C++, MFC
				\item \textbf{Synchronized Calendar} (2003 – 2004). Desktop calendar with globally shared and synchronized calendars, allowing users to schedule meetings with other users.  C\#.NET, SQL, XML
				\item \textbf{Operating System} (2002).  UNIX-style OS with scheduler, file system, text editor and calculator. C
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
				\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item JavaScript; Python; C++; C; Java; SQL; HTML; CSS; LESS; 
        \item Sublime Text; Linux (Debian, CentOS); Bash;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
